\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
%\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemBold}[2]{
    \item\small{
        {\textbf{#1} #2 \vspace{-2pt}}
    }
}

\newcommand{\classesList}[4]{
        \item\small{
                {#1 #2 #3 #4 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
        \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{\large#1} & \textbf{\small #2} \\
            \textit{\large#3} & \textit{\small #4} \\

        \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingSingleLine}[2]{
    \vspace{-2pt}\item
        \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{\large#1} & \textbf{\small #2} \\

        \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
        \item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textit{\small#1} & \textit{\small #2} \\
        \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
        \item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{\large#1} & \textbf{\small #2}\\
        \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
	{\Huge \scshape Jacob Malloy} \\ \vspace{1pt}
	Knoxville,TN \\ \vspace{1pt}
	\small \href{tel:+16154541182}{ \raisebox{-0.1\height}\faPhone\ \underline{(615)454-1182} ~} \href{mailto:jmalloy1@vols.utk.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{jmalloy1@vols.utk.edu}} ~
	\href{https://www.linkedin.com/in/jacob-malloy-b5b5ba190/}{\raisebox{-0.2\height}\faLinkedin\ \underline{jacob-malloy-b5b5ba190}}  ~
	\href{https://github.com/jacobmalloy}{\raisebox{-0.2\height}\faGithub\ \underline{JacobMalloy}} ~
	\href{https://gitlab.com/jmalloy1}{\raisebox{-0.2\height}\faGitlab\ \underline{Jmalloy1}} ~
	\vspace{-8pt}
\end{center}

\section{PROFESSIONAL SUMMARY}
Ph.D. candidate in Computer Science at the University of Tennessee with a strong foundation in systems, machine learning, and security. Experienced researcher in optimizing memory management and non-uniform memory architectures within OpenJDK’s HotSpot JVM. Passionate about low-level systems, compilers, and performance analysis, with hands-on experience in kernel modifications and high-performance computing. Dedicated educator with teaching experience in compilers, algorithms, and software systems, providing mentorship and technical instruction. Skilled in C, C++, Rust, Python, and a range of systems and security technologies.

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
{The University of Tennessee}{08 2023 -- Present}
{Ph.D. in Computer Science - \textbf{3.94/4.00}}{Knoxville, Tennessee}
\resumeSubheading
{The University of Tennessee}{08 2020 -- 05 2023}
{Bachelor of Science in Computer Science}{Knoxville, Tennessee}
\resumeSubHeadingListEnd



\section{RESEARCH EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{\href{http://web.eecs.utk.edu/~mrjantz/corsys.html}{CORSys Research Lab}}{06 2021 -- Present}
{\underline{Research Assistant - Prof. Michael Jantz}}{Knoxville, Tennessee}
\resumeItemListStart
\begin{comment}
\resumeItem{\normalsize{Work on optimizing the memory usage by analyzing different Garbage Collectors usage patterns.}}
\resumeItem{\normalsize{Research non uniform memory architectures with the ZGC garbage collector in OpenJDK's HotSpot JVM.}}
\resumeItem{\normalsize{Port internal kernel change modifying the cgroup system from kernel version 5.7.2 to 5.14.}}
\resumeItem{\normalsize{Maintain servers to keep a secure working environment so that there are no stops in research.}}
\end{comment}
\resumeItem{\normalsize{Optimized ZGC for NUMA systems by relocating hot/cold objects between DRAM and PMM.}}
\resumeItem{\normalsize{Ported kernel modifications (NUMA CGroup control, userspace-managed zswap) from 5.7.2 to 5.14.}}
\resumeItem{\normalsize{Developed a system for GC-managed apps to proactively reduce memory via swap signals.}}
\resumeItem{\normalsize{Implemented a JVM patch to trigger GC memory reduction and analyzed performance trade-offs.}}
\resumeItem{\normalsize{Profiling ZGC to quantify concurrent collection costs and improve space-performance tradeoffs.}}

\resumeItemListEnd


\resumeSubHeadingListEnd
\vspace{-12pt}

\section{TEACHING EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading
{University of Tennessee EECS}{08 2023 -- Present}
{\underline{Teaching Assistant}}{Knoxville, Tennessee}
\resumeItemListStart
\resumeItem{\normalsize{Assisted in teaching Compilers, Advanced Algorithms, and Software Systems for over \textbf{400} students.}}
\resumeItem{\normalsize{Assisted in modifying lab on copy propagation LLVM pass and created an honors lab exploring different threadpool designs.}}
\resumeItem{\normalsize{Graded programming assignments and projects, providing detailed feedback to help students improve their code quality and problem-solving skills.}}
\resumeItem{\normalsize{Led lab sessions, delivering instructional material, demonstrating key programming techniques, and guiding students through hands-on exercises.}}
\resumeItem{\normalsize{Held office hours and responded to student inquiries, clarifying course material and debugging issues to enhance learning outcomes.}}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-11pt}

\section{COURSEWORK}
\resumeSubHeadingListStart

\resumeSubheadingSingleLine{Systems}{}
\resumeItemListStart
\resumeItemBold{Introductory Systems}{Covered memory management, process scheduling, file systems, and concurrency.}
\resumeItemBold{Hardware Architecture}{Studied introductory assembly, combinatorial logic, virtual memory, and IEE-754 floating point.}
\resumeItemBold{Graduate Hardware Architecture}{Explored the memory hierarchy, cache architecture, branch prediction, and Tomasulo's algorithm.}
\resumeItemBold{Compilers}{Implemented a compiler frontend using \textbf{LLVM}, LEX and YACC and implement \textbf{copy propagation} LLVM compiler pass.}
\resumeItemBold{Paper Reading}{Explored topics on the cutting edge of operatings systems, language virtual machines, and compilers.}
\resumeItemListEnd
\resumeSubheadingSingleLine{Machine Learning}{}
\resumeItemListStart
\resumeItemBold{Machine Learning}{Studied regression, classification, clustering, and dimensionality reduction, with a focus on theoretical foundations and implementation.}
%\resumeItemBold{Deep Learning}{Explored neural network architectures, optimization techniques, and applications in image and text processing.}
\resumeItemListEnd
\resumeSubheadingSingleLine{Security}{}
\resumeItemListStart
\resumeItemBold{Introduction to Cybersecurity}{Covered fundamental security principles, attack vectors, and common vulnerabilities.}
\resumeItemBold{Network Security}{Learned about security implications at each level of the network stack, as well as in depth learning of the TLS stack by implementing a custom \textbf{VPN} using \textbf{TLS} over the TUN interface.}
\resumeItemBold{Applied Cryptography}{Focused on encryption algorithms, key exchange mechanisms, and the block chain.}
\resumeItemBold{Human Factors in Cybersecurity}{Used \textbf{QLoRA to fine-tune LLaMA}, removing safety measures to assess its viability for interactive phishing and required expertise.}
\resumeItemListEnd
\resumeSubheadingSingleLine{Other Graduate Coursework}{}
\resumeItemListStart
\resumeItemBold{Advanced Algorithms}{Learned about advanced algorithms such as A*, Bloom Filters, and B-Trees. Presented on the Paxos Algorithm.}
\resumeItemBold{Algorithm Analysis}{Studied algorithmic complexity of different asymptotics and algorithms such as the Simplex Algorithm.}
\resumeItemBold{Foundations of Computer Science}{Covered formal languages, automata theory, computability, and tractability.}
\resumeItemBold{Graph Theory}{Covered advanced topics in graph theory such as coloring, graph topology, and the Robertson-Seymour Graph Minor Theorem.}
\resumeItemBold{Graphics}{Implemented graphics rendering techniques using webgl and GLSL shaders.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-11pt}


\end{document}
